My Linux Notes

### 2018-07-29 Ubuntu_16.04_setup/mylinux.Rmd
up

@@

>>>>

Common Syntax
========

## Branching

### case
```bash
case "$var" in
	pattern_1)
		commands
		;;
	pattern_2)
		commands
		;;
esac
```

### if
```bash
if [[ ]]; then
	commands
elif [[ ]]; then
	commands
else
	commands
fi
```

## Loops

### for

#### With Sequence of Numbers

**Tradional Type**
```bash
for i in {1..3}; do
	commands
done
```

**C lang Type**
```bash
for (( i=0; i<=5; ++i )); do
	commands
done
```

#### Other Sequences

```bash
for i in A B C D; do
	commands
done
```

```bash
for i in {A..D}{1..3}; do
	commands
done
```

@@

## Parameter Expansions

### Match the last expresion
```{bash}
> ~/Desktop/foo.txt
file_path=~/Desktop/foo.txt
echo ${file_path##*/}
```
